Dragonfly Territory Ananlysis

### 2020-12-02 analysis/analysisSS.Rmd
figures exported from analysis, figures file added for clarity

>>>>

# number of species in chronological order
# I'll reuse the years vector I created earlier to make a data.frame

speciesChrono <- c(ASpecies, BSpecies, CSpecies, DSpecies, ESpecies, FSpecies, GSpecies, HSpecies, ISpecies, JSpecies, KSpecies, LSpecies, MSpecies, NSpecies, OSpecies, PSpecies, QSpecies, RSpecies, SSpecies, TSpecies, USpecies, VSpecies, XSpecies, YSpecies, ZSpecies, AASpecies, ABSpecies, ACSpecies, ADSpecies, AESpecies)

speciesByYear <- data.frame(YEAR, speciesChrono)

# look at it graphically

par(mfrow=c(1,1))
plot(speciesByYear$YEAR, speciesByYear$speciesChrono, xlab = "Year", ylab = "Species Number")
